### 2018-03-17 paper/7-related.tex
Minor tweaks around the bazel/buck non-det story

\item \Buck~\cite{buck} and \CloudBuild~\cite{esfahani2016cloudbuild} are both
fundamentally similar to \Bazel, differing around areas such as
non-determinism~\S\ref{sec-non-determinism}.

>>>>

\item \Buck~\cite{buck} is very similar to \Bazel. \CloudBuild~\cite{esfahani2016cloudbuild}
differs by allowing non-determinism~\S\ref{sec-non-determinism}, thus more closely modelling
our original definition of \Bazel from \S\ref{sec-implementation-bazel}.
